---
title: "Unit 5 HW"
author: "Nicole Wittlin"
date: "February 14, 2018"
output: 
    html_document:
      keep_md: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## QUESTION 1

### Part a: Import Text File (note, I created a csv file with the data to import)
```{r}
setwd("C:/Users/Nicole Wittlin/Documents/Classes/MSDS6306/Unit 5")
df <- read.csv("yob2016.csv", header=FALSE)
colnames(df)
colnames(df)[colnames(df) == "V1"] <- "Name"
colnames(df)[colnames(df) == "V2"] <- "Gender"
colnames(df)[colnames(df) == "V3"] <- "Count"
```

### Part b: Display Summary and Structure of Data
```{r}
summary(df)
str(df)
```

### Part c: Locate the duplicate data with "yyy"
```{r}
which(grepl("yyy", df$Name))
df[212,]
```

### Part d: Create y2016 data set
```{r}
y2016 <- subset(x=df, df$Name != "Fionayyy")
summary(y2016)
str(y2016)
```

## QUESTION 2

### Part a: Import Text File

```{r}
y2015 <- read.csv("yob2015.csv", header=FALSE)
colnames(y2015)
colnames(y2015)[colnames(y2015) == "V1"] <- "Name"
colnames(y2015)[colnames(y2015) == "V2"] <- "Gender"
colnames(y2015)[colnames(y2015) == "V3"] <- "Count"
```

### Part b: Final 10 rows
```{r}
tail(y2015, 10)
```
### It is interesting that all of these have a count of 5. I wonder if there was a minimum number of kids that needed to have the name to be included.

### Part c: Merge Data Sets
```{r}
Final <- merge(x=y2015, y=y2016, union("Name", "Gender"))
```

## QUESTION 3

### Part a: How many popular-named newborns?
```{r}
Final$Total <- (Final$Count.x + Final$Count.y)
head(Final)
sum(Final$Total)
```
### There were 7,239,231 newborns given popular names in 2015 and 2016.

### Part b: Most Popular Names 
```{r}
SortedFinal <- Final[order(-Final$Total),]
head(SortedFinal, 10)
```

### Part c: Most Popular Girls' Names
```{r}
JustGirls <- subset(x=SortedFinal, SortedFinal$Gender != "M")
head(JustGirls, 10)
```

### Part d: Write File of Names and Totals
```{r}
write.csv(JustGirls, file="FinalGirls.csv")
```
